---
title: "W_UP_03 Alcohol vs Seat choice"
author: "ediaz16"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library (tigerstats)
library (tidyverse)
data (ucdavis1)
davisdata = ucdavis1

```

# Introduction
 The research question is this: Is there a difference in the average amount of alcohol consumed per week by students whi sit in row 1, row 2, or row 3 of the UCdavis classroom

$H_0$: There is no difference between the average number of drinks imbibed between people based on the row they sit in.

$H_A$: The average number drinks is different between at least two rows. 
 
 
# Methods

Data from UC Davis: Seat is cateorical, and alcohol is numerical, so we use the Numerical~Cat helper file

# Description
## graphical description

```{r}
boxplot(alcohol~Seat,data=davisdata)
```

This boxplot shows that students who sit in the back row tend to drink more

# Graphical Results

# 
  
  
```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

## Inferential Tests

## Conclusions


