---
title: "W_UP_03 Alcohol vs Seat choice"
author: "ediaz16"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library (tigerstats)
library (tidyverse)
davisdata=read.csv('UCDavis.csv')


```

# Introduction
 The research question is this: Is there a difference in the average amount of alcohol consumed per week by students whi sit in row 1, row 2, or row 3 of the UCdavis classroom

$H_0$: There is no difference between the average number of drinks imbibed between people based on the row they sit in.

$H_A$: The average number drinks is different between at least two rows. 
 
 
# Methods

Data from UC Davis: Seat is cateorical, and alcohol is numerical, so we use the Numerical~Cat helper file

# Description
## graphical description

```{r}
boxplot(alcohol~Seat,data=davisdata)
```
# Graphical Results

This boxplot shows that students who sit in the back row tend to drink more

##numerical description 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

Numerical graph shows the median for back seat consumption is 3.5, front seat consumption is 0.0, and middle seat consumption is 1.0. Apparently those in the back seat drink more

##inferential description

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The P value is 0.000116 < 0.05 therefore we reject the $H_0$. That mean that all the students in the same ow do not consume the same amount on alcohol.

```{r}
plot(TukeyHSD(model1))
```

This graph shows the difference in alcohol the is no difference in the the middle to the front seat consumption and those in the back drink more than the middle and front row. 

#Conclution and Discussion

From box plot it appears that students who sit in the back row tend to drink more. From the inferential graph shows hat mean that all the students in the same ow do not consume the same amount on alcohol.From the tukey graph shows there is no difference in the the middle to the front seat consumption and those in the back drink more than the middle and front row. 
# 
  
  
```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

## Inferential Tests

## Conclusions


